HO unification from object language to meta language

### 2024-03-22 paper/main.tex
wip

This preliminary version of \elpiIn{comp} simply recognizes \Fo variables
applied to a (possibly empty) duplicate free list of names (i.e.
\elpiIn{pattern-fragment} detects variables in \llambda).

The auxiliary function \elpiIn{close-links} cannot be explained here,
che palle. \marginpar{fix}

@@

>>>>

This preliminary version of \elpiIn{comp} simply recognizes \Fo variables
applied to a (possibly empty) duplicate free list of names (i.e.
\elpiIn{pattern-fragment} detects variables in \llambda). Note tha compiling
\elpiIn{Ag} cannot create new mappings nor links, see the comp-lam hyp rule.

The auxiliary function \elpiIn{close-links}

@@

since we want links to bubble up we use the abs constructor of the inctx data
type to bind back the variable just crossed, and we do so only if the variable
v occurs in L.
